---
title: "Mouse DRG Doublet Finder Processing"
output: html_notebook
output_dir: "../data/doublet-finder-reports/"
params:
  sample: "110220DRG"
---

## Doublet Finder

Method for pK Identification without ground-truth calls using [DoubletFinder](https://github.com/chris-mcginnis-ucsf/DoubletFinder)

```{r echo=FALSE}
library(Seurat)
library(DoubletFinder)
library(tidyverse)
library(glue)
library(future)
options(future.globals.maxSize = +Inf)
plan(strategy = "multicore")
```

## Background

> Performs pN-pK parameter sweeps on a 10,000-cell subset of a
> pre-processed Seurat object. Will use all cells if Seurat object
> contains less than 10,000 cells. Results are fed into
> 'summarizeSweep' and 'find.pK' functions during optimal pK parameter
> selection workflow. Parameters tested: pN = 0.05-0.3, pK =
> 0.0005-0.3

 
```{r}
seur <- readRDS(glue("../data/objects/{params$sample}-filtered.RDS"))
seur <- NormalizeData(seur)
seur <- FindVariableFeatures(seur)
seur <- ScaleData(seur, features = rownames(seur), verbose = F)
seur <- RunPCA(seur, features = VariableFeatures(object = seur))
seur <- RunUMAP(seur, dims = 1:10)
DimPlot(seur, reduction = "umap")
```

```{r}
library(clustree)
seur <- FindNeighbors(seur, dims = 1:10)
seur <- FindClusters(seur, resolution = seq(0.1,1,0.1))
clustree(seur, prefix = "RNA_snn_res.")

sweep_res_list <- paramSweep_v3(seur, PCs = 1:10, sct = FALSE)
sweep_stats <- summarizeSweep(sweep_res_list, GT = FALSE)
bcmvn <- find.pK(sweep_stats)

# parse maximum pK
best_pk <- bcmvn[which(max(bcmvn$BCmetric)[[1]]==bcmvn$BCmetric),"pK"]
best_pk <- as.numeric(best_pk)
```


```{r}
UMAP_RESOLUTION <- 0.3
homotypic.prop <- modelHomotypic(seur@meta.data[[glue("RNA_snn_res.{UMAP_RESOLUTION}")]]) 
nExp_poi <- round(0.075*nrow(seur@meta.data))  ## Assuming 7.5% doublet formation rate - tailor for your dataset
nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))
print(glue("We define {nExp_poi.adj} homotypic doublets"))

# calculation with homotypic population estimates
xx <- doubletFinder_v3(seur, 
                       PCs = 1:10, 
                       pN = 0.25, 
                       pK = best_pk, 
                       nExp = nExp_poi.adj, 
                       reuse.pANN = FALSE, 
                       sct = FALSE)

df_class_name <- grep("DF.classification",names(xx@meta.data), value = T)
table(xx@meta.data[[df_class_name]])

dbl <- FetchData(xx,vars = df_class_name)
DimPlot(xx, reduction = "umap", group.by  = df_class_name)

# without homotypic calls
hh <- doubletFinder_v3(seur, 
                       PCs = 1:10, 
                       pN = 0.25, 
                       pK = best_pk, 
                       nExp = 0, 
                       reuse.pANN = FALSE, 
                       sct = FALSE)

df_class_name <- grep("DF.classification",names(hh@meta.data), value = T)
table(hh@meta.data[[df_class_name]])

dbl <- FetchData(hh,vars = df_class_name)
DimPlot(hh, reduction = "umap", group.by  = df_class_name)

```




